\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath, amssymb}
\usepackage{booktabs}
\usepackage{enumitem}

\title{Zero-Knowledge Regulatory Reporting:\\ zk-SNARK-Powered AML/CFT Compliance without Exposing Personal Transaction Data}
\author{Muhammad Anus \\ Universiti Teknologi Malaysia \\ Supervisor: Prof. Ts. Dr. MD Asri bin Ngadi}
\date{August 19, 2025}

\begin{document}
\maketitle

\begin{abstract}
We propose a regulatory reporting platform that enables AML/CFT verification using zero-knowledge proofs (zk-SNARKs). Regulated entities demonstrate compliance predicates (threshold limits, non-sanctioned status, and KYC membership) without revealing personal transaction data.
\end{abstract}

\section{Introduction}
Balancing privacy with AML/CFT is challenging. We explore zk-SNARKs to prove compliance predicates publicly while keeping private data secret.

\section{Model}
Public inputs: AML threshold, KYC Merkle root, Sanctions Merkle root, and a transaction commitment.
Private inputs: transaction amount, user attributes preimage, Merkle inclusion paths, and a flag proving non-membership in sanctions.

\section{Circuit Design}
We implement a Circom circuit with Poseidon commitments, inclusion proofs for KYC membership, and a constraint that the amount is at most the threshold. Sanctions non-membership uses a complement-trick: prover supplies a path proving membership of a disjoint commitment that implies exclusion (or uses a bit witness checked against a root).

\section{Verifier Integration}
We provide a CLI (snarkjs) and a Solidity registry contract to log compliance attestations. The on-chain verifier uses Groth16 verifying keys.

\section{Security and Limitations}
Trusted setup risks; stale roots; oracle integrity; front-running. Future work: recursive proofs, universal setup (Plonk/Halo2), velocity-based predicates, formal soundness proofs.

\section{Conclusion}
ZK proofs can enable compliance attestations without revealing PII, offering a promising path for privacy-preserving regulation.

\bibliographystyle{abbrv}
\begin{thebibliography}{9}
\bibitem{zkp} Bünz et al. \textit{Zether: Towards Privacy in Account-Based Cryptocurrencies}.
\bibitem{snarkjs} \texttt{snarkjs} documentation.
\bibitem{circom} \texttt{circom} documentation.
\end{thebibliography}

\end{document}
